Clustering time series based on probability distributions across temporal granularities

### 2021-11-15 main.Rmd

```{r cluster-number-selection-validation, fig.cap="sindex plotted as a function of the number of clusters for S1, S2, and S3. S1 has a sharp decrease in sindex from 5 to 6, whereas S2 and S3 have a decrease from 4 to 5. As a result, the number of clusters considered for S1, S2, and S3 is 5, 4, 4, respectively. This corresponds to the number of designs taken into account in each scenario.", eval=FALSE}
```

>>>>

```{r cluster-number-selection-validation, fig.cap="Separation index plotted as a function of the number of clusters for S1, S2, and S3. S1 has a sharp decrease from 5 to 6, whereas S2 and S3 have a decrease from 4 to 5. As a result, the number of clusters considered for S1, S2, and S3 is 5, 4, 4, respectively. This corresponds to the number of designs taken into account in each scenario."}
```
